### 2020-09-16 serial.tex
almost there

Recently, \cite{ali2020serial} also showed that serial intervals of COVID-19 decreased in China.

Our study underlines the importance of carefully defining measured epidemiological time distributions in general.
Previous studies have shown that it matters whether generation
intervals are measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
we generalize these ideas and show that they apply to other epidemiological distributions.
Some studies during the early phases of the COVID-19 epidemics

>>>>

Recently, \cite{ali2020serial} also showed that serial intervals of COVID-19 decreased in China. Analogous to our apporach, they also grouped serial intervals by the symptom onset date of infectors across 14-day periods and found that the mean serial interval decreased from 7.8 days to 2.6 days.
They attributed the decrease in serial intervals to reduction of the isolation delay period and showed that isolation delays can explain 51.5\% of the variation in serial intervals through a regression analysis.

More broadly, our study underlines the importance of carefully defining measured epidemiological time distributions.
Previous studies have shown that it matters whether generation
intervals are measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
we generalize these ideas and show that they apply to other epidemiological distributions.
Some studies during the early phases of the COVID-19 epidemics
